---
title: "Exclusive 'or'"
output: html_document
---

```{r setup, include = FALSE, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=5, 
                      echo=FALSE, warning=FALSE, message=FALSE)
require('ggplot2')
# require('plyr')
require('dplyr')
require('lme4')
require('gridExtra')
require('reshape2')

save = TRUE # whether to save plots
```

## Prepare data Exp 5

```{r, echo = TRUE}
  d5 <- read.csv("data5_080616.csv")
  d5 <- droplevels(filter(d5, !(language %in% c("Spanish"))))
  control5 <- d5[d5$condition == "test",]
  control5$distance <- ifelse(control5$trialType == "test_uncertain", 
                             abs(control5$answer - 0.5),
                             ifelse(control5$trialType == "test_false",
                                    control5$answer,
                                    1-control5$answer))
  loafers5 = control5 %>% group_by(id) %>% summarise(dist = sum(distance))
#   loafers5 <- ddply(
#     control5, c("id"), summarise,
#     dist = sum(distance)
#   )
  loafing_threshold5 = mean(loafers5$dist) + 2 * sd(loafers5$dist)
  bad_participants5 <- loafers5[loafers5$dist > loafing_threshold5,]$id
  d5 <- d5[!(d5$id %in% bad_participants5),]
  # d5 <- d5[(d5$id != "A2P065E9CYMYJL:3IXEICO793R2XURCARGYWH966VHT6V"),]
  d5$id <- factor(d5$id)
  cdata5 = subset(d5, d5$condition == "critical") %>% 
    group_by(name, type) %>%
    summarise(N       = length(answer),
      mean    = mean(answer),
      se.mean = sd(answer) / sqrt(N),
      se.RT   = sd(RT) / sqrt(N),
      RT      = mean(RT))
#   cdata5 <- ddply(
#       subset(d5, d5$condition == "critical"), c("name", "type"), summarise,
#       N       = length(answer),
#       mean    = mean(answer),
#       se.mean = sd(answer) / sqrt(N),
#       se.RT   = sd(RT) / sqrt(N),
#       RT      = mean(RT)
#   )
```
  
## Prepare data Exp 1

```{r, echo = TRUE}
  data <- read.csv("../01_xor-main/data2.csv")
  data <- droplevels(filter(data, !(language %in% c("Vietnamese", 
              "Spanish", 
              "Bengali, but I speak English as if I were a native speaker"))))
  data = droplevels(filter(data, name != "Bill's order"))
  control <- data[data$condition %in% c("test_uncertain", "test_false", "test_true"),]
  control$distance <- ifelse(control$condition == "test_uncertain", 
                             abs(control$answer - 0.5),
                             ifelse(control$condition == "test_false",
                                    control$answer,
                                    1-control$answer))
  loafers = control %>% group_by(id) %>% summarise(dist = sum(distance))
#   loafers <- ddply(
#     control, c("id"), summarise,
#     dist = sum(distance)
#   )
  loafing_threshold = mean(loafers$dist) + 2 * sd(loafers$dist)
  bad_participants <- loafers[loafers$dist > loafing_threshold,]$id
  data <- data[!(data$id %in% bad_participants),]
  data$id <- factor(data$id)
  cdata = data %>% 
    group_by(name, condition, type) %>%
    summarise(N = length(answer),
      mean    = mean(answer),
      se.mean = sd(answer) / sqrt(N),
      se.RT   = sd(RT) / sqrt(N),
      RT      = mean(RT))
#   cdata <- ddply(
#       data, c("name", "condition", "type"), summarise,
#       N       = length(answer),
#       mean    = mean(answer),
#       se.mean = sd(answer) / sqrt(N),
#       se.RT   = sd(RT) / sqrt(N),
#       RT      = mean(RT)
#   )
```

## Analysis

We construct a generalised linear model predicting proportions based on the average scores for each item and condition.

```{r echo = TRUE}
  rel.dp        <- cdata[cdata$condition == "rel",]$mean
  pri.dp        <- cdata[cdata$condition == "prior",]$mean
  com.dp        <- cdata[cdata$condition == "comp",]$mean
  priCon.dp        <- cdata5$mean
  names(rel.dp) <- cdata[cdata$condition == "rel",]$name
  names(pri.dp) <- cdata[cdata$condition == "prior",]$name
  names(com.dp) <- cdata[cdata$condition == "comp",]$name
  names(priCon.dp) <- cdata5$name
  data$rel      <- rel.dp[data$name]
  data$pri      <- pri.dp[data$name]
  data$com      <- com.dp[data$name]
  data$priCon      <- priCon.dp[data$name]

  xor <- data[data$condition == "xor",]

  model <- glm(answer ~ rel + pri + com + priCon, data = xor)
  
  summary(model)
```



## Correlation plot and correlation test

Per-vignette means of the prior ratings for conditional and conjunctive statements are highly correlated.

```{r fig.height = 3}
  xor.dp <- cdata[cdata$condition == "xor",]$mean
  df <- data.frame(xor = xor.dp, rel = rel.dp, com = com.dp, pri = pri.dp, priCon = priCon.dp)
  df$vignetteID = c("clothes", "dancing", "sunscreen", "squash", "graduate", "exams", "pet", "NY", "delay", "golf",
                    "drinking", "health", "lunch", "accident", "club")
  corPlot5 = ggplot(df, aes(x = pri, y = priCon)) + geom_point() + theme_bw() + geom_smooth(method = lm, se = TRUE) +
    geom_text(aes(label=vignetteID),hjust=0.5, vjust=-0.4, color = "firebrick", size = 2.5) + xlim(0,1) +
    xlab("mean conditional statements") + ylab("mean conjunctive statements")
  show(corPlot5)
  if (save) {
    ggsave(filename = "../../texts/01_paper_draft/pics/correlationPriorMeasuresExp1and5.pdf", plot = corPlot5, width = 3, height = 3)
  }

```

```{r}
cor.test(df$pri, df$priCon)
```


## Bayesian model comparison

```{r, message=FALSE, echo = TRUE}
require('BayesFactor')
bfsAll = generalTestBF(answer ~ rel + com + pri, data = xor)
bfsAllpriCon = generalTestBF(answer ~ rel + com + pri + priCon, data = xor)
bfspriCon = generalTestBF(answer ~ priCon, data = xor)
plot(bfsAllpriCon)
# if (save) {
#   pdf('../../texts/01_paper_draft/pics/bfsAll.pdf', height = 4, width = 6)
#   plot(c(bfspriCon, bfsAll))
#   dev.off()
#   }
```


## Combined plot of Exp 1 and 5

```{r}

dataPri = filter(data, condition == "prior") 
answerPri = 0

for (i in 1:(nrow(dataPri))) {
  dataSub = filter(dataPri, id == dataPri$id[i], name == dataPri$name[i])
  answerPri[i] = mean(dataSub$answer)
}
dataPri$answer = answerPri
dataPri = dataPri[(1:(nrow(dataPri)/2)) * 2 - 1 ,]

prepData = rbind(filter(data, condition != "prior"), dataPri)
combinedData1 = filter(prepData, condition %in% c("rel", "prior", "comp", "xor")) %>% 
  melt(measure.vars = c("answer"), id.vars = c("name", "type", "condition")) %>%
  mutate(condition = substr(condition, 1, 3))
combinedData5 = filter(d5, condition == "critical") %>% mutate(condition = "priCon") %>%
  melt(measure.vars = "answer", id.vars = c("name", "type", "condition"))
combinedData = rbind(combinedData1, combinedData5)
combinedData$value[combinedData$condition == "pri"] = 1 - combinedData$value[combinedData$condition == "pri"]
combinedData$value[combinedData$condition == "priCon"] = 1 - combinedData$value[combinedData$condition == "priCon"]

nameMap = function(x) {
  shortNames = c("clothes", "dancing", "sunscreen", "squash", "graduate", "exams", "pet", "NY", "delay", "golf",
                    "drinking", "health", "lunch", "accident", "club")
#   typeList = c("hlh", "hll", "lhh", "hhh", "llh", "hlh", "lll", "lll", "llh", "hll",
#                     "lhl", "hhh", "hhl", "hhl", "lhl")
  typeList = c("hll", "hlh", "lhl", "hhl", "lll", "hll", "llh", "llh", "lll", "hlh",
                    "lhh", "hhl", "hhh", "hhh", "lhh") # high prior => likely that "NOT (A and B)"
  longNames = levels(combinedData$name)
  paste(shortNames[which(longNames == x)], " (", typeList[which(longNames == x)], ")", sep = "", collapse = "")
}
nameMap = Vectorize(nameMap)
combinedData$name = factor(nameMap(x = combinedData$name),
                           levels = c("lunch (hhh)", "squash (hhl)", "dancing (hlh)", "club (lhh)", 
                                      "exams (hll)", "exams (lhl)", "NY (llh)", "delay (lll)", "sunscreen (lhl)",
                                      "accident (hhh)", "health (hhl)", "golf (hlh)", "drinking (lhh)", 
                                      "clothes (hll)", "pet (llh)", "graduate (lll)"))
combinedData$condition = factor(combinedData$condition, levels = c("xor", "rel", "com", "pri", "priCon"), ordered = TRUE)
cd = combinedData %>% group_by(name, condition) %>% 
  mutate(meanValueItem = mean(value))
cd = cd %>% group_by(condition) %>%
  mutate(meanValuePopulation = mean(value))

combinedBoxPlot = ggplot(cd, aes(x = condition, y = value, fill = condition)) + geom_boxplot() + facet_wrap(~ name, ncol = 8) +
  geom_point(aes(x = condition, y = meanValueItem, shape = "itemShape"), color = "black", size = 2.5) + 
  geom_point(aes(x = condition, y = meanValuePopulation, shape = "populationShape"), color = "black", size = 2.5 ) + 
  scale_shape_manual(name = 'means', 
         values =c('itemShape'= 4, 'populationShape' = 1), labels = c('per item','population'))
show(combinedBoxPlot)



```

## Regression to test relation of measures

To test whether the ratings of the conditionals sentences and those of the conjunctive sentences are any different, we look at a regression with dependent variable "Rating" and independent variables "vignette" and "measure type".

```{r}
regData = filter(combinedData, condition %in% c("pri", "priCon"))
bfsInd = generalTestBF(value ~ condition + name, data = regData)
plot(bfsInd)
show(bfsInd/bfsInd)
```


